\documentclass[13pt]{beamer}
%
% Choose how your presentation looks.
%
% For more themes, color themes and font themes, see:
% http://deic.uab.es/~iblanes/beamer_gallery/index_by_theme.html
%
\mode<presentation>
{
  \usetheme{CambridgeUS}     % or try Darmstadt, Madrid, Warsaw, ...
  \usecolortheme{beaver} % or try albatross, beaver, crane, ...
  \usefonttheme{default}  % or try serif, structurebold, ...
  \setbeamertemplate{navigation symbols}{}
  \setbeamertemplate{caption}[numbered]
} 

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{tikz}
\usepackage{tikz-uml}
\usepackage{hyperref}

\usepackage{listings}
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{myCustomCppStyle}{
  language=C++,
  numbers=left,
  stepnumber=1,
  numbersep=9pt,
  tabsize=2,
  showspaces=false,
  showstringspaces=false
}

\lstset{basicstyle=\tiny,style=myCustomCppStyle}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=1
}

\lstset{style=mystyle}

\usepackage{graphicx}
\graphicspath{ {./images/} }

\usepackage{tikz}
\usetikzlibrary{decorations.text}
\usetikzlibrary{shapes.geometric, arrows, positioning, calc, matrix}

\tikzset{
  basic box/.style={
    shape=rectangle, rounded corners, align=center,
    draw=#1, fill=#1!25},
  header node/.style={
    Minimum Width=header nodes,
    font=\strut\Large\ttfamily,
    text depth=+0pt,
    fill=white, draw},
  header/.style={%
    inner ysep=+1.5em,
    append after command={
      \pgfextra{\let\TikZlastnode\tikzlastnode}
      node [header node] (header-\TikZlastnode) at (\TikZlastnode.north) {#1}
      node [span=(\TikZlastnode)(header-\TikZlastnode)] at (fit bounding box) (h-\TikZlastnode) {}
    }
  },
  hv/.style={to path={-|(\tikztotarget)\tikztonodes}},
  vh/.style={to path={|-(\tikztotarget)\tikztonodes}},
  fat blue line/.style={ultra thick, blue}
}

\definecolor{mygray}{RGB}{208,208,208}
\definecolor{mymagenta}{RGB}{226,0,116}
\newcommand*{\mytextstyle}{\sffamily\Large\bfseries\color{black!85}}
\newcommand{\arcarrow}[3]{%
   % inner radius, middle radius, outer radius, start angle,
   % end angle, tip protusion angle, options, text
   \pgfmathsetmacro{\rin}{1.7}
   \pgfmathsetmacro{\rmid}{2.2}
   \pgfmathsetmacro{\rout}{2.7}
   \pgfmathsetmacro{\astart}{#1}
   \pgfmathsetmacro{\aend}{#2}
   \pgfmathsetmacro{\atip}{5}
   \fill[mygray, very thick] (\astart+\atip:\rin)
                         arc (\astart+\atip:\aend:\rin)
      -- (\aend-\atip:\rmid)
      -- (\aend:\rout)   arc (\aend:\astart+\atip:\rout)
      -- (\astart:\rmid) -- cycle;
   \path[
      decoration = {
         text along path,
         text = {|\mytextstyle|#3},
         text align = {align = center},
         raise = -1.0ex
      },
      decorate
   ](\astart+\atip:\rmid) arc (\astart+\atip:\aend+\atip:\rmid);
}
\title[Design Pattern]{Creational Design Pattern}
\author{Hung Tran}
\institute{Fpt software}
\date{\today}


\begin{document}

\begin{frame}
  \titlepage
\end{frame}

% Uncomment these lines for an automatically generated outline.
\begin{frame}{Outline}
  \tableofcontents
\end{frame}

\section{Creational Pattern Overview}

\begin{frame}{Creational Pattern Overview}
	\begin{center}
	\textcolor{blue}{\textbf{Construction process of an object.}}
	\end{center}
	\begin{itemize}
		\setlength\itemsep{1em}
		\item \textbf{Singleton}: Ensure only one instance.
		\item \textbf{Factory Method}: Create instance without depending on its concrete type.
		\item \textbf{Object pool}: Reuse existing instances.
		\item \textbf{Abstract factory}: Create instances from a specific family.
		\item \textbf{Prototype}: Clone existing objects from a prototype.
		\item \textbf{Builder}: Construct a complex object step by step.
	\end{itemize}
\end{frame}

\section{Factory Method pattern}

\begin{frame}{"new" operator problem}
\begin{columns}[T]
\begin{column}{.48\textwidth}
\lstset{basicstyle=\tiny,style=myCustomCppStyle}
\lstinputlisting{./examples/newOperator/newOperator.cpp}
\end{column}
\begin{column}{.48\textwidth}
	\begin{itemize}
		\setlength\itemsep{1em}
		\item Need name of class
		\item Tightly coupled with the name
		\item Add new class, modify the existing code
	\end{itemize}
\end{column}
\end{columns}
\end{frame}

\begin{frame}{The Intent of Factory Method Design Pattern}
	\begin{center}
	\textcolor{blue}{\textbf{Define an interface for creating an object, but let subclasses which class to instantitate. Factory method lets class defer instantiation to subclasses.}}
	\end{center}
\end{frame}

\begin{frame}{How to Implement of Factory Method Design Pattern?}
	\begin{itemize}
		\setlength\itemsep{1em}
		\item Different ways to implement
		\item An overridable method is provide that returns an instance of a class
		\item This method can be overridden to return instance of a subclass
		\item Behave likes constructor
		\item However, the constructor always returns the same instance
		\item The factory method can returns any sub-type 
		\item The factory method also called virtual constructor 
	\end{itemize}
\end{frame}

\begin{frame}{Structure of Singleton pattern?}
	\begin{center}
	\begin{tikzpicture}
	\umlemptyclass[type=abstract,x=0,y=0]{Product}
	\umlemptyclass[x=0,y=-3]{ConcreteProduct}
	\umlinherit{ConcreteProduct}{Product}
	
	\umlclass[type=abstract,x=4,y=0]{Creator}{}{\umlvirt{FactoryMethod()} \\ AnOperation()}
	\umlclass[x=4,y=-3]{ConcreteCreator}{}{FactoryMethod()}
	\umlinherit{ConcreteCreator}{Creator}
	\umlimport[geometry = -|-, weight = 0.3]{ConcreteCreator}{ConcreteProduct}
	\umlnote[x=8, y=-1, width = 4.2cm]{Creator}{product = FactoryMethod()}
	\umlnote[x=8, y=-4, width = 3.5cm]{ConcreteCreator}{return new concrete product}
	\end{tikzpicture}	
	\end{center}
\end{frame}

\begin{frame}{Basic implementation}
	\begin{center}
	\begin{tikzpicture}
	\umlemptyclass[type=abstract,x=0,y=0]{Product}
	\umlemptyclass[x=0,y=-3]{ConcreteProduct}
	\umlinherit{ConcreteProduct}{Product}
	
	\umlclass[type=abstract,x=4,y=0]{Creator}{}{\umlvirt{FactoryMethod()} \\ AnOperation()}
	\umlclass[x=4,y=-3]{ConcreteCreator}{}{FactoryMethod()}
	\umlinherit{ConcreteCreator}{Creator}
	\umlimport[geometry = -|-, weight = 0.3]{ConcreteCreator}{ConcreteProduct}
	\umlnote[x=8, y=-1, width = 4.2cm]{Creator}{product = FactoryMethod()}
	\umlnote[x=8, y=-4, width = 3.5cm]{ConcreteCreator}{return new concrete product}
	\end{tikzpicture}	
	\end{center}
\end{frame}

\begin{frame}{Pros and Cons}
\begin{columns}[T]
\begin{column}{.48\textwidth}
	\begin{center}
	\textcolor{blue}{\textbf{Pros}}
	\end{center}
	\begin{itemize}
		\setlength\itemsep{1em}
		\item Class itself control the instantiation process.
		\item Can allow multiple instances.
		\item Better than global variable.
		\item Can be subclassed.
	\end{itemize}
\end{column}
\begin{column}{.48\textwidth}
	\begin{center}
	\textcolor{blue}{\textbf{Cons}}
	\end{center}
		\begin{itemize}
		\setlength\itemsep{1em}
		\item Testing is difficult
		\item DCLP is defective
		\item Lazy destruction is complex
	\end{itemize}
\end{column}
\end{columns}
\end{frame}

\begin{frame}{Where to use?}
	\textcolor{blue}{When only one instance should be use because:}	
	\begin{itemize}
		\setlength\itemsep{1em}
		\item multiple instances cause data corruption.
		\item managing global state or shared state.
		\item multiple instances are not required.
	\end{itemize}
\end{frame}
\section{Factory Method}

\end{document}
